### 2016-11-09 sections/intro0.03.tex
V0.03; after thesis comments

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} 
% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
M31 has been observed by many telescopes including the {\textit {Hubble}}, \Spitzer and \Herschel space telescopes. %Els: Use the correct names for telescopes?
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the spatially-resolved SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

@@

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying structure of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.

@@

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect on each input on the position of the clusters in the SOM.
We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31 ones.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

>>>>

\section{Introduction} 
% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
M31 has a similar age, stellar mass, and morphological type to the Milky Way. 
Both galaxies are located in the ``green valley'' area in the colour versus stellar mass diagram of galaxies, which indicate they both lost most of their cold gas and hence have a low star formation rate.
In general M31 is considered a typical galaxy that is in a transition state from a starburst galaxy to a quiescent one \citep{Mutch11}.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
M31 has been observed by many telescopes including the {\textit {Hubble}}, \Spitzer and \Herschel space telescopes. %Els: Use the correct names for telescopes?
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the spatially-resolved SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

@@

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of machine learning/data mining algorithms and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying relation of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.

@@

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect on each input on the position of the clusters in the SOM.
We apply the 2D trained networks to the M101 data to study whether they have similar properties to M31.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.
